---
title: "fundamentalR_yuxin"
author: "Yuxin Bai"
date: "2024-02-24"
output: html_document
---

### Exercise 1: Use sum() to determine the sum of numbers from 2000 to 20000. Provide your code and the actual sum in your answer.
```{r}
sum(2000,20000)
```
The sum is 22000. 

### Exercise 2: In one or two sentences, describe what the below code snippet did.
```{r}
a <- 5
b <- 2:20
a
b
```
a<-5 will assign a with the number of 5 \
b<- 2:20 will create a list of 2 to 20 and assign to object b \
a will let R show the number associated with object a \
b will let R show the list associated with object b \


### Exercise 3: Add the contents of a and b together and place the results in a new object. Examine the result. Include your code. Try using both sum() and +; do you get different results? If so, why?
```{r}
a+b
sum(a,b)
```
I get different results. \
a+b will add 5 to every numbers in the list b, and then generate a list from 2+5 to 20+5. The sum function will add object a and every number in the object b together to give me a sum. 

### Exercise 4: What is the sum of the 5th through 10th element of object b? Provide your code and the sum.

```{r}
sum(b[5]:b[10])
```
The sum is 51

### Exercise 5: What is the sum of the 3rd, 8th, and 10th element of b?
```{r}
sum(b[3], b[8], b[10])
```
The sum is 24


### Exercise 6: When extracting from a 2-dimensional object, which number specifies rows and which specifies columns? What does m[3,] do? How can you extract the 3rd, 4th and 5th columns of m together as one object?
```{r}
m <- matrix(data=1:25,ncol=5,byrow=T)
m
m[3,]
```
The **first** number specify **row**, and the **second** number specifies **column**. \
m[3,] will extract the whole row 3 from the matrix. \
The code below will extract column 3, 4, 5 of m together as one object. 

```{r}
m[,3:5]
```


### Exercise 7: What does the cbind command do? How about rbind? Create a new object “n” where the first row is a new row of numbers (your choice) and the following rows are the rows from matrix m. Optional: do the same but reverse the order of the rows from matrix m.
```{r}
cbind(m,101:105)
```
cbind command will combine the objects by column. In the code above, cbind will combine matrix m with 1 list of 101 to 105 by column. \
rbind will combine the objects by row. 
```{r}
n<-rbind(51:55,m)
n

n2<-rbind(51:55,m[5:1,])
n2
```






